Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-04-01 fmics/paper.tex
minor revisions in section 1

The SRS component has a complex structure and the correctness of its behaviour is critical for safe and productive use of the LHC.
Any error in the SRS implementation would either compromise the availability of the LHC (unnecessary request for beam dump) or safety (not triggering a necessary beam dump).
The current approach for analyzing the SRS implementation relies on the simulation of its behavior on sample streams of input for different loss scenarios~\cite{Chris-thesis}.

In this paper, we describe a formal verification approach based on logical deduction, using HOL4 theorem prover~\cite{HOL4,DBLP:conf/tphol/SlindN08}, for analyzing the SRS implementation.
Our high level proof strategy takes advantage of the regular structure of the SRS, which consists of multiple layers of shift registers and some simple arithmetic hardware.
There is a degree of regularity in how the output of each layer is used as input to the next layer.
There is also a degree of regularity in the timing of each layer with respect to its position in the stack of layers.
This regularity serves as a basis for inductive reasoning, which makes the amount of verification effort impervious to the number of layers in the structure.

>>>>

The SRS component has a complex structure and the correctness of its behaviour is critical for safe and productive use of the LHC.
Any error in the SRS implementation would compromise either the availability of the LHC (unnecessary request for a beam dump) or its safety (not triggering a necessary beam dump).
The current approach for analyzing the SRS implementation is simulation of its behavior on sample streams of input for different loss scenarios~\cite{Chris-thesis}.

In this paper, we describe a formal verification approach, based on logical deduction using HOL4 theorem prover~\cite{HOL4,DBLP:conf/tphol/SlindN08}, to analyzing the SRS implementation.
Our high level proof strategy takes advantage of the regular structure of the SRS, which consists of multiple layers of shift registers and some simple arithmetic hardware.
There is a degree of regularity in how the output of each layer is used as input to the next layer.
There is also a degree of regularity in the timing of each layer with respect to its position in the stack of layers.
This regularity serves as a basis for inductive reasoning, which makes the amount of verification effort impervious to the number of layers in the structure.
